Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-16 papers/B1555_EdgeOn/B1555_letter.tex
change template to MNRAS

\documentclass[manuscript]{emulateapj}

\usepackage{color}
\definecolor{simonacolor}{cmyk}{0, 0.9808, 0.4429, 0.1412}
\newcommand{\simona}[1]{\textcolor{simonacolor}{#1}}

\shorttitle{Beware the Effect of Edge-on Disks}
\shortauthors{Hsueh et al.}

\begin{document}

\title{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author{TBD}

\begin{abstract}
With the latest infrared image of B1555+375, an edge-on disk is shown to over cross the strong lensed images. Indicating the flux ratio anomalie of B1555+375 is dominanted by its edge-on disk structure. We present a lens model with SIE bulge and exponential disk, base on the radio observation from \citet{Marlow}. And apply this model to SHARP infrared image.

\end{abstract}

\keywords{ gravitaional lensing}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane.  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to understand
this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group.  
This process is challenging
due to the faintness of the satellite galaxies.  Furthermore, lower-mass
satellites may not be able to retain the gas needed for ongoing star
formation \citep[e.g.,][]{P11}, rendering them effectively dark.
These factors make gravitational \simona{lensing a powerful and promising tool for the detection of substructure.}

\simona{It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
\simona{Indeed,} little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
\simona{Moreover, unlike in the optical or infrared,} in the radio band, lensed images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
\simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}. While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}. Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.}

While future large-scale surveys, such as the LSST, \simona{are
  expected to deliver new large samples of gravitationally lensed
  quasar, in the near future the discovery of new systems using}
narrow-line quasar emission \citep{N14} \simona{will provide new
  invaluable statistical perspective on current constraints based on
  flux ratio anomalies.  In this paper, we explore the alternative
  idea that flux ratio anomalies are not related to the presence of
  substructure but originate in a more complex lens galaxy mass
  distribution than initially considered. To this end we use new
  infra-red data from the Strong lensing at High Angular Resolution
  Program(SHARP). The main goal of the SHARP} project \simona{is to
  re-observe} known quadruple and Einstein ring lens systems at a much
higher angular resolution by making use of the Keck adaptive optics
(AO) telescope and large interferometric arrays \citep{SHARP12,V12}
. In particular, to better understand the cause of flux ratio
anomalies in strong lens systems \simona{we focus on the lens
  modelling of the lens system B1555+375 (included in both the
  observational and theoretical analysis of \citet{Dalal2002} and
  \citet{Xu14}, respectively) by making use of} the new information
obtained from the latest SHARP infrared imaging. \simona{The paper is
  organized as follows: the latest SHARP data is introduced in section
  2; in section 3 we present the lens model while the results of this
  analysis and their implication are discussed in section 4.}

@@

\begin{figure*}
\plotone{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
%
\label{fig:multiband}}
\end{figure*}

@@

\begin{figure}
\plotone{1555_ao_merlin_overlay.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
%
\label{fig:merlin}}
\end{figure}

@@

@@

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this new information from A/O image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

%\begin{figure}
%\plotone{B1555_Kp.eps}
%\plottwo{B1555_model.eps}{B1555_residue.eps}
%\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
%An edge-on disk can be seen in the center of SHARP K-band image. Exponential disk is marked by the green ellipse in residue image. We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
%\end{figure}
%
%\begin{figure}
%\plotone{point_source.eps}
%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
%\end{figure}

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{ccccccc}
%%\tableline\tableline
		&SIE+Expdisk& 2-SIE		   
\\
\tableline\tableline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$92.90$ &	$95.05$	  \\
$M_{tot} / \sigma_2$& $1.17\times 10^{10} $  &$81.36$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\tableline

\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Subscripts 1 and 2 represent bulge and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}

%%table2
\begin{table}
\begin{center}
\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-2}}
\begin{tabular}{lccccc}
\tableline\tableline
					&Radio	&		 & Model-predicted \\
Component &East &North &East 		&North\\ 
\tableline
A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$   \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.}
\end{center}
\end{table}

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lccccc}
\tableline\tableline
				&5 GHz & 15 GHz  &Model-predicted\\
\tableline
A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
A/C 		&$2.0$ 	&$2.4$ &$2.2$  \\
A/D			&$13.0$ &$ 12.9$ & $8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.}
\end{center}
\end{table}

We then use an extended source to model SHARP infrared image. In Figure 1, B and D have no detection in K-band, which believed due to strong dust extinction from the edge-on disk. The region and orientation of exponential disk in lens model are consistent with this hypothesis. The flux ratios in infrared are much higher than in radio also supports as an evidence of dust extinction.

@@

\bibliographystyle{apj}
\bibliography{reference.bib}

%\begin{thebibliography}{}
%\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
%\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
%\end{thebibliography}

>>>>

% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

\documentclass[useAMS,usenatbib]{mn2e}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author[Jen-Wei Hsueh and A. N. Other]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$University of California, Davis, Davis 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}

\maketitle

\label{firstpage}

\begin{abstract}
With the latest infrared image of B1555+375, an edge-on disk is shown to over cross the strong lensed images. Indicating the flux ratio anomalie of B1555+375 is dominanted by its edge-on disk structure. We present a lens model with SIE bulge and exponential disk, base on the radio observation from \citet{Marlow}. And apply this model to SHARP infrared image.
\end{abstract}

\begin{keywords}
gravitaional lensing.
\end{keywords}

@@

	A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane.  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to understand
this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group.  
This process is challenging
due to the faintness of the satellite galaxies.  Furthermore, lower-mass
satellites may not be able to retain the gas needed for ongoing star
formation \citep[e.g.,][]{P11}, rendering them effectively dark.
These factors make gravitational lensing a powerful and promising tool for the detection of substructure.

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
Moreover, unlike in the optical or infrared, in the radio band, lensed images are not sensitive to micro lensing from stars nor dust extinction. 
This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}. While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure. An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}. Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are
  expected to deliver new large samples of gravitationally lensed
  quasar, in the near future the discovery of new systems using
narrow-line quasar emission \citep{N14} will provide new
  invaluable statistical perspective on current constraints based on
  flux ratio anomalies.  In this paper, we explore the alternative
  idea that flux ratio anomalies are not related to the presence of
  substructure but originate in a more complex lens galaxy mass
  distribution than initially considered. To this end we use new
  infra-red data from the Strong lensing at High Angular Resolution
  Program(SHARP). The main goal of the SHARP project is to
  re-observe known quadruple and Einstein ring lens systems at a much
higher angular resolution by making use of the Keck adaptive optics
(AO) telescope and large interferometric arrays \citep{SHARP12,V12}
. In particular, to better understand the cause of flux ratio
anomalies in strong lens systems we focus on the lens
  modelling of the lens system B1555+375 (included in both the
  observational and theoretical analysis of \citet{Dalal2002} and
  \citet{Xu14}, respectively) by making use of the new information
obtained from the latest SHARP infrared imaging. The paper is
  organized as follows: the latest SHARP data is introduced in section
  2; in section 3 we present the lens model while the results of this
  analysis and their implication are discussed in section 4.

@@

\begin{figure*}
\begin{minipage}{140mm}
%\includegraphics[width=84mm]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
%
\end{minipage}

\end{figure*}

\begin{table}
 \centering
 %\begin{minipage}{140mm}
  \caption{Multiband observation details of the B1555+375 lens system.}
  \begin{tabular}{@{}llccc}

\hline
  Telescope     &      Camera     &  Band & Date &$t_{exp}$ (s) \\

 \hline
   HST				&		WFPC2    &  F555W		&	2009/01/20	&	5200\\
   HST				&		WFPC2    &  F814W		&	2009/01/20&	5200\\
   HST				&		NICMOS/NIC2	&	F160W	&	2012/08/09 & 5376\\
   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
   \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
%
\label{fig:merlin}}
\end{figure}

@@

The observation details of Keck AO and HST imaging are shown in Table 1.

@@

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. The from the edge-on disk can explain why there is no detection of image B \& D in near-infrared (Fig 1, right). Its orientation is aligned with image B \& D. With this new information from AO image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 3, Table 3 \& 4.

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$92.90$ &	$95.05$	  \\
$M_{tot} / \sigma_2$& $1.17\times 10^{10} $  &$81.36$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\hline
\end{tabular}

%\end{minipage}
\medskip
Subscripts 1 and 2 represent bulge and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. $e$ is ellipticity and $\theta$ is the position angle measured east of north.

\end{table}

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Radio observation and model-predicted lensed image positions.}
  \begin{tabular}{@{}ccccc}

\hline

Component	&\multicolumn{2}{c}{MERLIN}		 & \multicolumn{2}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&			\\
					 &East &North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$   \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
\hline
\end{tabular}

%\end{minipage}
\medskip
Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.

\end{table}

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Flux ratios of B1555+375 components.}
  \begin{tabular}{@{}ccccc}

\hline
Flux ratio	& \multicolumn{2}{c}{MERLIN} & Model\\
		&5 GHz & 15 GHz  &\\
\hline
A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
A/C 		&$2.0$ 	&$2.4$ &$2.2$  \\
A/D			&$13.0$ &$ 12.9$ & $8.0$  \\

\hline
\end{tabular}

%\end{minipage}
\medskip
Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.

\end{table}

@@

\section*{Acknowledgments}

\bibliographystyle{mn2e}
\bibliography{reference.bib}

\label{lastpage}
